### 2012-07-24 docs/architecture/architecture.tex
move special bottom solver section to mg/

\maestro\ uses the multigrid solver to enforce the divergence constraint
both on the half-time edge-centered advective velocities (the ``MAC
projection'') and on the final cell-centered velocities (the ``HG
projection'').  For the MAC projection, since the velocity data is
edge-centered (the MAC grid), the projection is cell-centered.  For
the HG projection, since the velocity data is cell-centered, the
projection is node-centered.  \MarginPar{should draw a figure} The multigrid solver performs a number
of V-cycles until the residual drops by 10-12 orders-of-magnitude.
There are several options that affect how the multigrid solver
behaves, which we describe below.

\subsection{Special Bottom Solver}
We have a special bottom solver type that greatly speeds up large problems
and speeds up smaller problems to a lesser degree.
In fact, you should use this bottom solver whenever possible, because I
have yet to find a case that performs worse than our standard bottom solver.
What this special solver essentially does is take the data from the coarsest 
level of the original multigrid V-cycle and copy it onto a new grid structure 
with the same number of total cells in each direction, but with a fewer number of larger 
grids.  A new V-cycle begins from this point, 
so we are essentially coarsening this ``new'' problem.
Now, the coarsest level of the multigrid V-cycle in the ``new'' problem has 
fewer cells and fewer grids as compared to the original coarsest level.

To enable this solver, set {\tt hg\_bottom\_solver = 4} (for the nodal
projections) and/or {\tt mg\_bottom\_solver = 4} (for the cell-centered
projections) in your inputs file.

To understand how this bottom solver works, the first thing you need to know
is what the grid structure of the coarsest level of your multigrid V-cycle
looks like (we need to put a description of this in the section above).
Now, figure out the size of the box you would need if you
wanted it to fit all the data on the coarsest level.  Now, figure out what
the largest integer $n$ is so that you can evenly divide the length of this box
by $2^n$ in every coordinate direction.  If $n < 2$, the program will abort
since the grid structure is not suitable for this bottom solver.

Now the code will set up a ``new'' problem, using the data at the coarsest level
of the original problem as the initial data.  The grid structure for this new
problem has the same number of cells as the coarsest level of the original problem,
but the data is copied onto a grid structure where each grid has $2^n$ cells
on each side.  The new V-cycle continues down to the new coarsest level, in
which each grid has 2 cells on each side.  If you wish to impose a limit on
the maximum value that $n$ can have, you can do so by setting 
{\tt max\_mg\_bottom\_nlevs} equal to that value.

{\bf Example 1:} A 3D problem with $384^3$ cells divided into $32^3$ grids, i.e., 
there is a $12\times 12\times 12$ block of $32^3$ grids.  The coarsest level of the 
multigrid V-cycle contains $12\times 12\times 12$ grids that have $2^3$ cells, so the 
entire problem domain has $24^3$ cells.  We see that $n=3$, and create a new problem 
domain with a $3\times 3\times 3$ block of $8^3$ grids.  The coarsest level of the 
multigrid V-cycle for the ``new'' problem will be a $3\times 3\times 3$ block of 
$2^3$ grids.

{\bf Example 2:} A 2D problem with $96\times 384$ cells divided into $48^2$ grids, i.e., 
there is a $2\times 8$ block of $48^2$ grids.  The coarsest level of the multigrid 
V-cycle contains $2\times 8$ grids that have $3^2$ cells, so the entire problem 
domain has $6\times 24$ cells.  We see that $n=1$, so the program aborts since this grid
structure is not appropriate for the fancy bottom solver.

>>>>

\maestro\ uses the multigrid solver to enforce the divergence
constraint both on the half-time edge-centered advective velocities
(the ``MAC projection'') and on the final cell-centered velocities
(the ``HG projection'').  For the MAC projection, since the velocity
data is edge-centered (the MAC grid), the projection is cell-centered.
For the HG projection, since the velocity data is cell-centered, the
projection is node-centered.  \MarginPar{should draw a figure} The
multigrid solver performs a number of V-cycles until the residual
drops by 10-12 orders-of-magnitude.  There are several options that
affect how the multigrid solver behaves, which we describe below.
More detail on the multigrid solvers is given in Chapter~\ref{ch:mg}.

### 2012-07-24 docs/mg/mg.tex
move special bottom solver section to mg/

@@

>>>>

\label{ch:mg}

@@

\subsection{Special Bottom Solver}
We have a special bottom solver type that greatly speeds up large problems
and speeds up smaller problems to a lesser degree.
In fact, you should use this bottom solver whenever possible, because I
have yet to find a case that performs worse than our standard bottom solver.
What this special solver essentially does is take the data from the coarsest 
level of the original multigrid V-cycle and copy it onto a new grid structure 
with the same number of total cells in each direction, but with a fewer number of larger 
grids.  A new V-cycle begins from this point, 
so we are essentially coarsening this ``new'' problem.
Now, the coarsest level of the multigrid V-cycle in the ``new'' problem has 
fewer cells and fewer grids as compared to the original coarsest level.

To enable this solver, set {\tt hg\_bottom\_solver = 4} (for the nodal
projections) and/or {\tt mg\_bottom\_solver = 4} (for the cell-centered
projections) in your inputs file.

To understand how this bottom solver works, the first thing you need to know
is what the grid structure of the coarsest level of your multigrid V-cycle
looks like (we need to put a description of this in the section above).
Now, figure out the size of the box you would need if you
wanted it to fit all the data on the coarsest level.  Now, figure out what
the largest integer $n$ is so that you can evenly divide the length of this box
by $2^n$ in every coordinate direction.  If $n < 2$, the program will abort
since the grid structure is not suitable for this bottom solver.

Now the code will set up a ``new'' problem, using the data at the coarsest level
of the original problem as the initial data.  The grid structure for this new
problem has the same number of cells as the coarsest level of the original problem,
but the data is copied onto a grid structure where each grid has $2^n$ cells
on each side.  The new V-cycle continues down to the new coarsest level, in
which each grid has 2 cells on each side.  If you wish to impose a limit on
the maximum value that $n$ can have, you can do so by setting 
{\tt max\_mg\_bottom\_nlevs} equal to that value.

{\bf Example 1:} A 3D problem with $384^3$ cells divided into $32^3$ grids, i.e., 
there is a $12\times 12\times 12$ block of $32^3$ grids.  The coarsest level of the 
multigrid V-cycle contains $12\times 12\times 12$ grids that have $2^3$ cells, so the 
entire problem domain has $24^3$ cells.  We see that $n=3$, and create a new problem 
domain with a $3\times 3\times 3$ block of $8^3$ grids.  The coarsest level of the 
multigrid V-cycle for the ``new'' problem will be a $3\times 3\times 3$ block of 
$2^3$ grids.

{\bf Example 2:} A 2D problem with $96\times 384$ cells divided into $48^2$ grids, i.e., 
there is a $2\times 8$ block of $48^2$ grids.  The coarsest level of the multigrid 
V-cycle contains $2\times 8$ grids that have $3^2$ cells, so the entire problem 
domain has $6\times 24$ cells.  We see that $n=1$, so the program aborts since this grid
structure is not appropriate for the fancy bottom solver.
